---
title: "Boston-House-Price-Prediction"
author: "RAHUL RAWAT"
date: "2022-09-27"
output: html_document
---

------------------------------------------------------------------------

<b><span style = "color:green;font-size:25px;">
<center><u>MULTIPLE LINEAR REGRESSION ON BOSTON HOUSE PRICE PREDICITON DATASET</u></center>

</span></b>

<p style="color:MediumSeaGreen;">

<b> The Boston Housing Dataset is a derived from information collected by the U.S. Census Service concerning housing in the area of Boston MA. The following describes the dataset columns -: </b>

</p>

```{=html}
<pre>
<center><b style = "color:green;font-size:18px;">Objective - To predict the price of the house from these features</b>

<b style = "color:#FFA07A">MODEL  - <u>MUILTIPLE LINEAR REGRESSION</u>
   TARGET VARIABLE - MEDV
LIBRARIES - "tidyverse","corrplot","lattice","caTools","plotly","MASS"</b></center>
<b><hr></b>
<center><b style = "color:green;font-size:18px;"><u>DATASET DESCRIPTION</u></b></center>
The dataset describes how the house price might vary depending on several features
<b><u>The information of the features considered</u></b> -
      1. CRIM   -:per capita crime rate by town
      2. ZN     -:proportion of residential land zoned for lots over 25,000 sq.ft.
      3. INDUS  -:proportion of non-retail business acres per town.
      4. CHAS   -:Charles River dummy variable (1 if tract bounds river; 0 otherwise)
      5. NOX    -:nitric oxides concentration (parts per 10 million)
      6. RM     -:average number of rooms per dwelling
      7. AGE    -:proportion of owner-occupied units built prior to 1940
      8. DIS    -:weighted distances to five Boston employment centres
      9. RAD    -:index of accessibility to radial highways
     10. TAX    -:full-value property-tax rate per $10,000
     11. PTRATIO-:pupil-teacher ratio by town
     12. B      -:1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town
     13. LSTAT  -:% lower status of the population
     14. MEDV   -:Median value of owner-occupied homes in $1000's
<b><hr></b>
<center><b><u style = "color:green;font-size:18px;">THE STEPS FOLLOWED IN THE PROCESS OF MULTIPLE LINEAR REGRESSION</u></b></center>
 -> Importing packages mentioned and the dataset
 -> computing the descriptive statistics
 -> performed exploratory data analysis
 -> data quality and remediation
        <b>1. checking for null vaues - found none
        2. replaced outliers
        3. duplicates              - found none</b>
 -> split the dataset into training and testing data
 -> building the model on the training dataset 
 -> examine the summary of the model
 -> after getting the best R2 score possible, predict the values for the training data and compute the Root mean square 
    error
 -> predict the values for the testing data and compute the root mean square error
 -> Inference
</pre>
```
<h2>

<b>

<center><u>IMPORTING LIBRARIES</u></center>

</b>

</h2>

```{=html}
<style type='text/css'>
  body 
  {
    background-color:lavender
   }
  h2 
  { color :Chili Peppe;
    font-family:times
   }
</style>
```
```{r}
#install.packages(c("tidyverse","corrplot","lattice","caTools","plotly","MASS"))
library(MASS)
library(tidyverse)
library(lattice)
library(corrplot)
library(plotly)
library(caTools)
library(Metrics)
library(beeswarm)

# Reading the dataset
Boston = read.csv("project/boston housing/boston.csv")

# Display top 6 rows of the datasets
head(Boston)

# getting the information about dataframe
str(Boston)

# Getting the shape of dataset ( means number of rows and column)
dim(Boston)
                                  
#SUMARRY
summary(Boston)     

```

<h2>

<b>

<center><u>BOXPLOT</u></center>

</b>

</h2>

```{=html}
<style>
h2{
color :red;
font-family:times
}
</style>
```
```{r}
##BOXPLOT

CRIM = Boston$CRIM
ZN   = Boston$ZN
INDUS = Boston$INDUS
CHAS  = Boston$CHAS
NOX   = Boston$NOX
RM    = Boston$RM
AGE   = Boston$AGE
DIS   = Boston$DIS
RAD   = Boston$RAD
TAX   = Boston$TAX
PTRATIO  = Boston$PTRATIO
B   = Boston$B
LSTAT = Boston$LSTAT
MEDV = Boston$MEDV

##BOXPLOT

plot_ly(y = CRIM,name = "CRIM",type = "box")%>%
  add_boxplot(y = ZN,name = "ZN",type = "box")%>%
  add_boxplot(y = INDUS,name = "INDUS",type = "box")%>%
  add_boxplot(y = CHAS,name = "CHAS",type = "box")%>%
  add_boxplot(y = NOX,name = "NOX",type = "box")%>%
  add_boxplot(y = RM,name = "RM",type = "box")%>%
  add_boxplot(y = AGE,name = "AGE",type = "box")


plot_ly(y = DIS,name = "DIS",type = "box")%>%
  add_boxplot(y = RAD,name = "RAD",type = "box")%>%
  add_boxplot(y = TAX,name = "TAX",type = "box")%>%
  add_boxplot(y = PTRATIO,name ="PTRATIO",type = "box")%>%
  add_boxplot(y = B,name ="B",type = "box")%>%
  add_boxplot(y = LSTAT,name = "LSTAT",type = "box")%>%
  add_boxplot(y = MEDV,name = "MEDV",type = "box")

#### Columns Like CRIM,ZN,RM,B seems to have outliers.Lets see the outliers percentage in every columns
# CRIM
Q1_CRIM = quantile(CRIM,probs= 0.25);Q1_CRIM
Q3_CRIM = quantile(CRIM,probs = 0.75);Q3_CRIM
IQR_CRIM = IQR(CRIM);IQR_CRIM
UP_CRIM = Q3_CRIM+ (1.5*IQR_CRIM);UP_CRIM
LW_CRIM = Q1_CRIM- (1.5*IQR_CRIM);LW_CRIM
CRIM1 = CRIM[which(CRIM >= UP_CRIM)]
length(CRIM1)

# ZN   
Q1_ZN = quantile(ZN,probs= 0.25);Q1_ZN
Q3_ZN = quantile(ZN,probs = 0.75);Q3_ZN
IQR_ZN = IQR(ZN);IQR_ZN
UP_ZN = Q3_ZN+ (1.5*IQR_ZN);UP_ZN
LW_ZN = Q1_ZN- (1.5*IQR_ZN);LW_ZN
ZN1 = ZN[which(ZN >= UP_ZN)]
length(ZN1)

# INDUS      
Q1_INDUS = quantile(INDUS,probs= 0.25);Q1_INDUS
Q3_INDUS = quantile(INDUS,probs = 0.75);Q3_INDUS
IQR_INDUS = IQR(INDUS);IQR_INDUS
UP_INDUS = Q3_INDUS+ (1.5*IQR_INDUS);UP_INDUS
LW_INDUS = Q1_INDUS- (1.5*IQR_INDUS);LW_INDUS
INDUS1 = INDUS[which(INDUS >= UP_INDUS)]
length(INDUS1)
  
# CHAS    
Q1_CHAS = quantile(CHAS,probs= 0.25);Q1_CHAS
Q3_CHAS = quantile(CHAS,probs = 0.75);Q3_CHAS
IQR_CHAS = IQR(CHAS);IQR_CHAS
UP_CHAS = Q3_CHAS+ (1.5*IQR_CHAS);UP_CHAS
LW_CHAS = Q1_CHAS- (1.5*IQR_CHAS);LW_CHAS
CHAS1 = CHAS[which(CHAS >= UP_CHAS)]
length(CHAS1)
      
# NOX
Q1_NOX = quantile(NOX,probs= 0.25);Q1_NOX
Q3_NOX = quantile(NOX,probs = 0.75);Q3_NOX
IQR_NOX = IQR(NOX);IQR_NOX
UP_NOX = Q3_NOX+ (1.5*IQR_NOX);UP_NOX
LW_NOX = Q1_NOX- (1.5*IQR_NOX);LW_NOX
NOX1 = NOX[which(NOX >= UP_NOX)]
length(NOX1)

# RM    
Q1_RM = quantile(RM,probs= 0.25);Q1_RM
Q3_RM = quantile(RM,probs = 0.75);Q3_RM
IQR_RM = IQR(RM);IQR_RM
UP_RM = Q3_RM+ (1.5*IQR_RM);UP_RM
LW_RM = Q1_RM- (1.5*IQR_RM);LW_RM
RM1 = RM[which(RM >= UP_RM)]
RM2 = RM[which(RM <= LW_RM)]
length(RM1)
length(RM2)

# AGE      
Q1_AGE = quantile(AGE,probs= 0.25);Q1_AGE
Q3_AGE = quantile(AGE,probs = 0.75);Q3_AGE
IQR_AGE = IQR(AGE);IQR_AGE
UP_AGE = Q3_AGE+ (1.5*IQR_AGE);UP_AGE
LW_AGE = Q1_AGE- (1.5*IQR_AGE);LW_AGE
AGE1 = AGE[which(AGE >= UP_AGE)]
length(AGE1)

# DIS      
Q1_DIS = quantile(DIS,probs= 0.25);Q1_DIS
Q3_DIS = quantile(DIS,probs = 0.75);Q3_DIS
IQR_DIS = IQR(DIS);IQR_DIS
UP_DIS = Q3_DIS+ (1.5*IQR_DIS);UP_DIS
LW_DIS = Q1_DIS- (1.5*IQR_DIS);LW_DIS
DIS1 = DIS[which(DIS >= UP_DIS)]
length(DIS1)

# RAD      
Q1_RAD = quantile(RAD,probs= 0.25);Q1_RAD
Q3_RAD = quantile(RAD,probs = 0.75);Q3_RAD
IQR_RAD = IQR(RAD);IQR_RAD
UP_RAD = Q3_RAD+ (1.5*IQR_RAD);UP_RAD
LW_RAD = Q1_RAD- (1.5*IQR_RAD);LW_RAD
RAD1 = RAD[which(RAD >= UP_RAD)]
length(RAD1)

# TAX      
Q1_TAX = quantile(TAX,probs= 0.25);Q1_TAX
Q3_TAX = quantile(TAX,probs = 0.75);Q3_TAX
IQR_TAX = IQR(TAX);IQR_TAX
UP_TAX = Q3_TAX+ (1.5*IQR_TAX);UP_TAX
LW_TAX = Q1_TAX- (1.5*IQR_TAX);LW_TAX
TAX1 = TAX[which(TAX >= UP_TAX)]
length(TAX1)

# PTRATIO      
Q1_PTRATIO = quantile(PTRATIO,probs= 0.25);Q1_PTRATIO
Q3_PTRATIO = quantile(PTRATIO,probs = 0.75);Q3_PTRATIO
IQR_PTRATIO = IQR(PTRATIO);IQR_PTRATIO
UP_PTRATIO = Q3_PTRATIO+ (1.5*IQR_PTRATIO);UP_PTRATIO
LW_PTRATIO = Q1_PTRATIO- (1.5*IQR_PTRATIO);LW_PTRATIO
PTRATIO1 = PTRATIO[which(PTRATIO >= UP_PTRATIO)]
PTRATIO2 = PTRATIO[which(PTRATIO <= LW_PTRATIO)]
length(PTRATIO1)
length(PTRATIO2)

# B
Q1_B = quantile(B,probs= 0.25);Q1_B
Q3_B = quantile(B,probs = 0.75);Q3_B
IQR_B = IQR(B);IQR_B
UP_B = Q3_B+ (1.5*IQR_B);UP_B
LW_B = Q1_B- (1.5*IQR_B);LW_B
B1 = B[which(B >= UP_B)]
B2 = B[which(B <= LW_B)]
length(B1)
length(B2)

# LSTAT
Q1_LSTAT = quantile(LSTAT,probs= 0.25);Q1_LSTAT
Q3_LSTAT = quantile(LSTAT,probs = 0.75);Q3_LSTAT
IQR_LSTAT = IQR(LSTAT);IQR_LSTAT
UP_LSTAT = Q3_LSTAT+ (1.5*IQR_LSTAT);UP_LSTAT
LW_LSTAT = Q1_LSTAT- (1.5*IQR_LSTAT);LW_LSTAT
LSTAT1 = LSTAT[which(LSTAT >= UP_LSTAT)]
length(LSTAT1)

# MEDV
Q1_MEDV = quantile(MEDV,probs= 0.25);Q1_MEDV
Q3_MEDV = quantile(MEDV,probs = 0.75);Q3_MEDV
IQR_MEDV = IQR(MEDV);IQR_MEDV
UP_MEDV = Q3_MEDV+ (1.5*IQR_MEDV);UP_MEDV
LW_MEDV = Q1_MEDV- (1.5*IQR_MEDV);LW_MEDV
MEDV1 = MEDV[which(MEDV >= UP_MEDV)]
MEDV2 = MEDV[which(MEDV <= LW_MEDV)]
length(MEDV1)
length(MEDV2)

print(paste("Column CRIM outliers = ",length(CRIM1)*100/506,"%"))
print(paste("Column ZN outliers = ",length(ZN1)*100/506,"%"))
print(paste("Column INDUS outliers = ",length(INDUS1)*100/506,"%"))
print(paste("Column CHAS outliers = ",length(CHAS1)*100/506,"%"))
print(paste("Column NOX outliers = ",length(NOX1)*100/506,"%"))
print(paste("Column RM outliers = ",(length(RM1)+length(RM2))*100/506,"%"))
print(paste("Column AGE outliers = ",length(AGE1)*100/506,"%"))
print(paste("Column DIS outliers = ",length(DIS1)*100/506,"%"))
print(paste("Column RAD outliers = ",length(RAD1)*100/506,"%"))
print(paste("Column TAX outliers = ",length(TAX1)*100/506,"%"))
print(paste("Column PTRATIO outliers = ",(length(PTRATIO2)+length(PTRATIO1))*100/506,"%"))
print(paste("Column B outliers = ",(length(B1) + length(B2))*100/506,"%"))
print(paste("Column LSTAT outliers = ",length(LSTAT1)*100/506,"%"))
print(paste("Column MEDV outliers = ",(length(MEDV1) +length(MEDV2))*100/506,"%"))

        
```
<h2>
<b>
<center><u>HISTOGRAM AND DISTRIBUTION</u></center>
</b>
</h2>
```{r}
par(mfrow = c(1,3))
#CRIM
hist(CRIM,prob = TRUE)
lines(density(CRIM),col = "blue",lwd = 2)

#ZN
hist(ZN,prob = TRUE)
lines(density(ZN),col = "blue",lwd = 2)

#INDUS
hist(INDUS,prob = TRUE)
lines(density(INDUS),col = "blue",lwd = 2)

#CHAS
hist(CHAS,prob = TRUE)
lines(density(CHAS),col = "blue",lwd = 2)

#NOX
hist(NOX,prob = TRUE)
lines(density(NOX),col = "blue",lwd = 2)

#RM
hist(RM,prob = TRUE)
lines(density(RM),col = "blue",lwd = 2)

#AGE
hist(AGE,prob = TRUE)
lines(density(AGE),col = "blue",lwd = 2)

#DIS
hist(DIS,prob = TRUE)
lines(density(DIS),col = "blue",lwd = 2)

#RAD
hist(RAD,prob = TRUE)
lines(density(RAD),col = "blue",lwd = 2)

#TAX
hist(TAX,prob = TRUE)
lines(density(TAX),col = "blue",lwd = 2)

#PTRATIO
hist(PTRATIO,prob = TRUE)
lines(density(PTRATIO),col = "blue",lwd = 2)

#B
hist(B,prob = TRUE)
lines(density(B),col = "blue",lwd = 2)

#LSTAT
hist(LSTAT,prob = TRUE)
lines(density(LSTAT),col = "blue",lwd = 2)

#MEDV
hist(MEDV,prob = TRUE)
lines(density(MEDV),col = "blue",lwd = 2)

```
<h3><b>The histogram also shows that columns CRIM, ZN, B has highly skewed distributions. Also MEDV looks to have a normal distribution (the predictions) and other colums seem to have norma or bimodel ditribution of data except CHAS (which is a discrete variable)</b></h3>
<style>
h3{
color :red;
font-size : 280%;
font-family:times
}
</style>

<h2>
<b>
<center><u>CORRELATION</u></center>
</b>
</h2>

```{=html}
<style>
h2{
color :red;
font-family:times
}
</style>
```
```{r}
#CORRELATION

corrmatrix = cor(Boston)
corrmatrix
corrplot(corrmatrix)


```

<h2>

<b>

<center><u>Crime Analysis In Boston</u></center>

</b>

</h2>

```{=html}
<style>
h2{
color :Blue;
font-family:times
}
</style>
```
```{r}


summary(Boston$CRIM)
plot_ly(data = Boston,x =~LSTAT,y =~CRIM,type= "scatter",mode = "markers")
plot_ly(data = Boston,x =~RAD,y =~CRIM,type= "scatter",mode = "markers")
plot_ly(data = Boston,x =~TAX,y =~CRIM,type= "scatter",mode = "markers")
quantile(Boston$CRIM,0.9)
highcrime = subset(Boston,CRIM>quantile(Boston$CRIM,0.9))
highcrime
summary(highcrime)
plot_ly(data = highcrime,x =~LSTAT,y =~CRIM,type= "scatter",mode = "markers")
plot_ly(data = Boston,y = ~LSTAT,name = "FULL BOSTON DATA",type = "box")%>%
  add_boxplot(data = highcrime,y = ~LSTAT,name = "Area with 90% percentile crime rate(highcrime",type = 'box')

plot_ly(data = Boston,y = ~MEDV,name = "FULL BOSTON DATA",type = "box")%>%
  add_boxplot(data = highcrime,y = ~MEDV,name = "Area with 90% percentile crime rate(highcrime",type = 'box')

summary(Boston)
```

<h2 style="color:Tomato;">

<b>Portion of Population with Lower Status Analysis</b>

</h2>

<p>

From the correlation matrix we can see that there are significant levels of correlation between LSTAT and these variables:

```{=html}
<pre>
1.MEDV : negative correlation coefficient
2.RM   : negative correlation coefficient
3.AGE  : positive correlation coefficient
</pre>
```
```{r}
corrmatrix
plot_ly(data = Boston,x=~LSTAT,y=~MEDV,type = "scatter",mode = "markers")
plot_ly(data = Boston,x=~LSTAT,y=~RM,type = "scatter",mode = "markers")
plot_ly(data = Boston,x=~LSTAT,y=~AGE,type = "scatter",mode = "markers")

# THOSE AREAS WHICH ARE ABOVE THE 90TH PERCENTILE OF LSTAT
summary(Boston$LSTAT)
quantile(Boston$LSTAT,0.9)
highlstat = subset(Boston,LSTAT>quantile(Boston$LSTAT,0.9))

plot_ly(data = Boston,y = ~MEDV,name = "FULL BOSTON DATA",type = "box")%>%
  add_boxplot(data = highlstat,y = ~MEDV,name = "Area with 90% percentile LSTAT",type = 'box')

plot_ly(data = Boston,y = ~RM,name = "FULL BOSTON DATA",type = "box")%>%
  add_boxplot(data = highlstat,y = ~RM,name = "Area with 90% percentile LSTAT",type = 'box')

plot_ly(data = Boston,y = ~AGE,name = "FULL BOSTON DATA",type = "box")%>%
  add_boxplot(data = highlstat,y = ~AGE,name = "Area with 90% percentile LSTAT",type = 'box')

plot_ly(data = Boston,y = ~CRIM,name = "FULL BOSTON DATA",type = "box")%>%
  add_boxplot(data = highlstat,y = ~CRIM,name = "Area with 90% percentile LSTAT",type = 'box')

plot_ly(data = Boston,y = ~NOX,name = "FULL BOSTON DATA",type = "box")%>%
  add_boxplot(data = highlstat,y = ~NOX,name = "Area with 90% percentile LSTAT",type = 'box')
```

<h2 style="color:Tomato;">

<b><u> LINEAR REGRESSION </u></b>

</h2>

```{r}
##SIMPLE LINEAR REGRESSION

####any(is.na(Boston))
####numb = length(which(is.na(Boston) == TRUE))
####if (numb>0){
####  Boston = Boston[complete.case(Boston),]
####}
####numb

set.seed(0)
split = sample.split(Boston,SplitRatio = 0.8)

train = subset(Boston,split == TRUE)
test  = subset(Boston,split == FALSE)

head(train)

model = lm(MEDV~LSTAT,data = train)
summary(model)

pred = predict(model,test)
rmse(pred,test[,14])

data = data.frame(LSTAT = (1:30),MEDV = predict(model,data.frame(LSTAT=(1:30))))
plot_ly() %>% add_trace(x = ~LSTAT,y = ~MEDV,type = "scatter",mode = "lines",data = data,name ="Predicted Value")%>%
  add_trace(x = ~LSTAT,y = ~MEDV,type = "scatter",mode = "markers",data = test,name ="Predicted Value")

```

<h4 style="color:Tomato;">

<b> POLYNOMIAL REGRESSION </b>

</h4>

```{r}

model = lm(MEDV~LSTAT + I(LSTAT^2),data = train)
summary(model)

pred = predict(model,test)
rmse(pred,test[,14])

data = data.frame(LSTAT = (1:35),MEDV = predict(model,data.frame(LSTAT=(1:35))))
plot_ly() %>% add_trace(x = ~LSTAT,y = ~MEDV,type = "scatter",mode = "lines",data = data,name ="Predicted Value")%>%
  add_trace(x = ~LSTAT,y = ~MEDV,type = "scatter",mode = "markers",data = test,name ="Predicted Value")
 
```

<h5 style="color:Tomato;">

<b> POLYNOMIAL REGRESSION </b>

</h5>

```{r}
model = lm(MEDV~LSTAT + I(LSTAT^2)+I(LSTAT^3),data = train)
summary(model)

pred = predict(model,test)
rmse(pred,test[,14])

data = data.frame(LSTAT = (1:35),MEDV = predict(model,data.frame(LSTAT=(1:35))))
plot_ly() %>% add_trace(x = ~LSTAT,y = ~MEDV,type = "scatter",mode = "lines",data = data,name ="Predicted Value")%>%
  add_trace(x = ~LSTAT,y = ~MEDV,type = "scatter",mode = "markers",data = test,name ="Predicted Value")

summary(model)
plot(model)
```

<h1 style="color:Tomato;">

<b> MULTIPLE REGRESSION MODEL </b>

</h1>

```{r}
model = lm(MEDV~LSTAT + I(LSTAT^2)+I(LSTAT^3)+RM+CRIM+AGE+DIS+RAD+TAX+PTRATIO+B,data = train)
summary(model)

pred = predict(model,test)
rmse(pred,test[,14])

summary(model)
plot(model)


```

```{r}
model = lm(MEDV~LSTAT + I(LSTAT^2)+RM+CRIM+DIS+RM+TAX+PTRATIO+B,data = train)
summary(model)

pred = predict(model,test)
rmse(pred,test[,14])

summary(model)
plot(model)

```

<h3>MODEL AFTER REMOVING THE OUTLIERS</h3>
```{r}
##### LSTAT

LSTAT1 = LSTAT[!(LSTAT >= UP_LSTAT | LSTAT <= LW_LSTAT)]
View(LSTAT1)
length(LSTAT1)


par(mfrow = c(1,2))
plot(LSTAT)          
abline(h = UP_LSTAT,col ="blue")               
abline(h = LW_LSTAT,col = "red")               
abline(h = LW_LSTAT,col = "red")


new_boston1 = Boston[Boston$LSTAT<= UP_LSTAT,]
dim(new_boston1)
view(new_boston1)

boxplot(LSTAT)
boxplot(LSTAT1)
plot(LSTAT1)
abline(h = UP_LSTAT,col="blue")

#PTRATIO
PTRATIO1 = PTRATIO[!(PTRATIO >= UP_PTRATIO | PTRATIO <= LW_PTRATIO)]
View(PTRATIO1)
length(PTRATIO1)


par(mfrow = c(1,2))
plot(PTRATIO)          
abline(h = UP_PTRATIO,col ="blue")               
abline(h = LW_PTRATIO,col = "red")
plot(PTRATIO1)
abline(h = UP_PTRATIO,col="blue")               
abline(h = LW_PTRATIO,col = "red")


new_boston2 = new_boston1[new_boston1$PTRATIO >=  LW_PTRATIO,]
dim(new_boston2)
view(new_boston2)

boxplot(PTRATIO)
boxplot(PTRATIO1)

#DIS
DIS1 = DIS[!(DIS >= UP_DIS | DIS <= LW_DIS)]
View(DIS1)
length(DIS1)


par(mfrow = c(1,2))
plot(DIS)          
abline(h = UP_DIS,col ="blue")               
abline(h = LW_DIS,col = "red")
plot(DIS1)
abline(h = UP_DIS,col="blue")               
abline(h = LW_DIS,col = "red")


new_boston3 = new_boston2[new_boston2$DIS <=  UP_DIS,]
dim(new_boston3)
view(new_boston3)

boxplot(DIS)
boxplot(DIS1)

#CRIM
par(mfrow = c(1,3))
plot(CRIM)
plot(CRIM[which(CRIM >= UP_CRIM)])
abline(h = UP_CRIM,col = "blue")
abline(h = LW_CRIM,col = "red")
new_CRIM = replace(new_boston3$CRIM,which(new_boston3$CRIM >= UP_CRIM),UP_CRIM);length(new_CRIM)
plot(new_CRIM)
abline(h = UP_CRIM,col = "blue")
abline(h = LW_CRIM,col = "red")

new_boston3$CRIM = new_CRIM
boxplot(new_boston3$CRIM)

#RM

par(mfrow = c(1,3))
plot(RM)
abline(h = UP_RM,col = "blue")
abline(h = LW_RM,col = "red")
plot(RM[which(RM >= UP_RM)])
abline(h = UP_RM,col = "blue")
abline(h = LW_RM,col = "red")
new_RM = replace(new_boston3$RM,which(new_boston3$RM >= UP_RM),UP_RM);length(new_RM)
new_RM1 = replace(new_RM,which(new_RM <= LW_RM),LW_RM);length(new_RM1)
plot(new_RM1)
abline(h = UP_RM,col = "blue")
abline(h = LW_RM,col = "red")

new_boston3$RM = new_RM1
boxplot(new_boston3$RM)

#ZN
boxplot(ZN)
par(mfrow = c(1,3))
plot(ZN)
abline(h = UP_ZN,col = "blue")
abline(h = LW_ZN,col = "red")
plot(ZN[which(ZN >= UP_ZN)])
abline(h = UP_ZN,col = "blue")
abline(h = LW_ZN,col = "red")
new_ZN = replace(new_boston3$ZN,which(new_boston3$ZN >= UP_ZN),UP_ZN);length(new_ZN)
plot(new_ZN)
abline(h = UP_ZN,col = "blue")
abline(h = LW_ZN,col = "red")

new_boston3$ZN = new_ZN
plot(new_boston3$ZN)

#B
boxplot(new_boston3$B)

par(mfrow = c(1,3))
plot(B)
plot(B[which(B <= LW_B)])
abline(h = UP_B,col = "blue")
abline(h = LW_B,col = "red")
new_B = replace(new_boston3$B,which(new_boston3$B <= LW_B),LW_B);length(new_B)
plot(new_B)
abline(h = UP_B,col = "blue")
abline(h = LW_B,col = "red")

new_boston3$B = new_B
boxplot(new_boston3$B)

Boston = new_boston3
dim(Boston)
```


